% blue-eyed-puzzle.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
  \begin{exampleblock}{The Blue-eyed Islanders Puzzle}
    There is an island upon which a tribe resides. \pause
    The tribe consists of 1000 people, with various eye colours. \pause
    Yet, \red{\bf their religion forbids them to know their own eye color,
    or even to discuss the topic}; \pause
    thus, each resident can (and does) see the eye colors of all other residents,
    but has no way of discovering his or her own (there are no reflective surfaces). \pause
    If a tribesperson does discover his or her own eye color,
    then their religion compels them to
    \blue{\bf commit ritual suicide at noon the following day in the village square
    for all to witness}. \pause
    All the tribespeople are \cyan{\bf highly logical and devout},
    and they all know that each other is also highly logical and devout
    (and they all know that they all know that each other is highly logical and devout,
    and so forth).
  \end{exampleblock}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
  \begin{exampleblock}{}
    Of the 1000 islanders,
    it turns out that \teal{\bf 100 of them have blue eyes and 900 of them have brown eyes},
    although the islanders are not initially aware of these statistics
    (each of them can of course only see 999 of the 1000 tribespeople). \pause\\[6pt]

    One day, a \purple{\bf blue-eyed foreigner} visits to the island
    and wins the complete trust of the tribe. \pause\\[6pt]

    One evening, he addresses the entire tribe to thank them
    for their hospitality. \pause\\[6pt]

    However, not knowing the customs,
    the foreigner makes the mistake of mentioning eye color in his address,
    remarking ``\teal{\bf how unusual it is to see another blue-eyed person
    like myself in this region of the world''}. \pause\\[6pt]

    \violet{\bf What effect, if anything, does this {\it faux pas} have on the tribe?}
  \end{exampleblock}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
  \begin{center}
    The foreigner \red{\bf has no effect}, \pause \\[6pt]
    because his comments do \blue{\bf not} tell the tribe anything \\[6pt]
    that they do not already know \pause \\[15pt]
    (everyone in the tribe can already see that \\[6pt]
    there are several blue-eyed people in their tribe).
  \end{center}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
  \begin{center}
    \red{\bf 100 days after the address, \\[6pt]
    all the blue eyed people commit suicide.}

    \pause
    \vspace{0.80cm}
    \begin{theorem}[The Blue-eyed Islanders Puzzle]
      \begin{center}
        Suppose that the tribe had $n > 0$ blue-eyed people. \\[6pt]
        Then $n$ days after the traveller's address, \\[6pt]
        all $n$ blue-eyed people commit suicide.
      \end{center}
    \end{theorem}
  \end{center}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
  \begin{center}
    \red{By induction on the number $n$ of blue-eyed people in the tribe.}

    \pause
    \vspace{0.80cm}
    \begin{description}
      \setlength{\itemsep}{8pt}
      \item[基础步骤:] $n = 1$. \\
        \uncover<3->{这个唯一的蓝眼人的内心独白: 你直接念我身份证吧}
      \item[归纳假设:] 假设命题对 $n$ 个蓝眼人的情况也成立。
      \item[归纳步骤:]
        \uncover<5->{}
    \end{description}
  \end{center}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%